
\subsubsection{Italian} %\textbf{Also here, add data-set sizes.}
%\textbf{For the examples, you know the linguex packet, right?}
%\textbf{Given that you itemize by gender, can you add a baseline based
%  on picking the most frequent variant of the noun/adjective?}
% We focus on paradigms where gender and number are explicitly and
% systematically encoded and it is possible to compare same-length
% strings. We are able to extract enough stimuli that never occur in the
% training corpus, so that an n-gram control would be at chance
% level. Moreover, by experiment construction, baselines relying on
% unigram frequency are also at chance level.

\paragraph{Article-noun gender agreement}
%(1) eadj-aonoun:

Similar to German, Italian articles agree with the noun in gender;
however, Italian has a relatively extended paradigm of masculine and
feminine nouns differing only in the final vowel (-\emph{o} and
-\emph{a}, respectively), allowing us to test agreement in fully
controlled paradigms such as the following:

\ex.\ag. \{\underline{il},\ la\}  congeniale  candidato \\
the congenial candidate\ (m.) \\
\bg.  \{il,\ \underline{la}\}  congeniale  candidata \\
the congenial candidate\ (f.) \\
%\begin{enumerate}[label={(\arabic*)}]
%	\item 
%		\begin{tabular}[t]{lllllll}
%	a. & \{\underline{il}, la\} & congeniale & candidato \\
%   &  the & congenial & candidate (m.) \\
%	& \multicolumn{4}{l}{`The congenial male candidate.'} \\
%	b. & \{il, \underline{la}\} & congeniale & candidata \\
%    &the & congenial & candidate (f.) \\
%	& \multicolumn{4}{l}{`The congenial female candidate.'} \\
%\end{tabular}
%\end{enumerate}

The intervening adjective, ending in -\emph{e}, does not cue
gender. We constructed the stimuli with words appearing at least 100
times in the training corpus. We required moreover the \emph{-a}
and \emph{-o} forms of a noun to be reasonably balanced in frequency
(neither form is more than twice as frequent as the other), or both rather
frequent (appear at least 500 times). As the prenominal adjectives are
somewhat marked, we only considered -\emph{e} adjectives that occur
prenominally with at least 10 distinct nouns in the training corpus.
Here and below, stimuli were manually checked removing nonsensical
adjective-noun (below, adverb-adjective) combinations. Finally, adjective-noun combinations that
occurred in the training corpus were excluded, so that an n-gram
baseline would perform at chance level. We obtained 15,005 stimulus
pairs in total. % In
% addition to CNLMs and WordNLM, we tested frequency baseline choosing
% the option with the higher unigram probability (whole-stimulus corpus
% frequencies are at chance by construction).
35.8\% of them contained an adjective or noun that was
OOV for the WordNLM. Again, we report this model's results on its
full-coverage subset, where the CNLM performance is only slightly above
the one reported.

Results are shown on the first line of
Table \ref{tab:ital-agr-results}.  WordNLM shows the strongest
performance, closely followed by the LSTM CNLM.  The RNN CNLM
performs strongly above chance (50\%), but again lags behind the LSTM.

\paragraph{Article-adjective gender agreement}
We next consider agreement between articles and adjectives with an intervening adverb:
\ex.\ag. il meno \{\underline{alieno},\ aliena\} \\
the\ (m.) less alien\ one \\
\bg. la meno \{alieno,\ \underline{aliena}\} \\
the\ (f.) less alien\ one \\

%\begin{enumerate}[label={(\arabic*)}]
%	\item 
%		\begin{tabular}[t]{lllllll}
%	a. & il & meno & \{ \underline{alieno}, aliena \} \\
%   &  the (m.)& less & alien  \\
%	b. & la & meno & \{ alieno, \underline{aliena} \} \\
%    &the (f.)& less & alien one \\
%\end{tabular}
%\end{enumerate}
where we used the adverbs \emph{pi{\`u}} `more', \emph{meno} `less',
\emph{tanto} `so much'. We considered only adjectives that occurred 1K
times in the training corpus (as adjectives ending in \emph{-a}/\emph{-o} are
very common). We excluded all cases in which the
adverb-adjective combination occurred in the training corpus, obtaining 88 stimulus pairs. Due to the restriction to common adjectives, there were no WordNLM OOVs. %
%
%Here and in the next experiment, the frequency baseline chose the version with the more common adjective.
% /checkpoint/mbaroni/char-rnn-exchange/candidate_adv_aoadj_testset.txt
Results are shown on the second line of
Table~\ref{tab:ital-agr-results}; all three models perform almost
perfectly.  Possibly, the task is made easy by the use of extremely common
adverbs and adjectives.

\begin{table}[t]
  \begin{small}
    \begin{center}
      \begin{tabular}{l|ll|c}
        & \multicolumn{2}{c|}{CNLM} & \multicolumn{1}{c}{\multirow{2}{*}{WordNLM}}\\
        &\emph{LSTM}&\emph{RNN} &  \\ \hline
% eadj-aonoun
        Noun Gender & 93.1  & 79.2 & 97.4\\
%      adv-aoadj
        Adj.~Gender & 99.5 & 98.9 & 99.5\\
% adv-aeadj
        Adj.~Number & 99.0 & 84.5 & 100.0\\
%	    & \multicolumn{4}{c|}{CNLM} & \multicolumn{2}{c|}{\multirow{2}{*}{WordNLM}}  & \multicolumn{2}{c}{\multirow{2}{*}{Frequency}}\\
%	    &\multicolumn{2}{c|}{\emph{LSTM}}&\multicolumn{2}{c|}{\emph{RNN}} & & & \\ \hline
%% eadj-aonoun
%	    Noun Gender & 96.6&89.6  & 84.4&73.9 & 99.1&95.6 & 100.0 & 0.0\\
%%      adv-aoadj
%	    Adj.~Gender & 98.9&100.0 & 100.0&97.8 & 98.9&100.0 & 55.7 & 44.3 \\
%% adv-aeadj
%	    Adj.~Number & 99.0&99.0 & 99.0&70.0 & 100.0&100.0 & 86.7 & 13.3 \\
%
      \end{tabular}
    \end{center}
  \end{small}
  \caption{\label{tab:ital-agr-results} Italian agreement results. Random baseline accuracy is 50\% in all three experiments.} % For each model and test, we report percentage accuracy on two stimulus classes (masculine/feminine for gender, singular/plural for number).}
\end{table}

% \begin{table}[t]
%   \begin{small}
%     \begin{center}
%       \begin{tabular}{l|ll|l|l}
%         & \multicolumn{2}{c|}{CNLM} & \multicolumn{1}{c|}{\multirow{2}{*}{WordNLM}}  & \multicolumn{1}{c}{\multirow{2}{*}{Freq.}}\\
%         &\emph{LSTM}&\emph{RNN} &  \\ \hline
% % eadj-aonoun
%         Noun Gender & 93.1  & 79.2 & 97.4 & 50.0\\
% %      adv-aoadj
%         Adj.~Gender & 99.5 & 98.9 & 99.5 & 50.0\\
% % adv-aeadj
%         Adj.~Number & 99.0 & 84.5 & 100.0 & 50.0 \\
% %	    & \multicolumn{4}{c|}{CNLM} & \multicolumn{2}{c|}{\multirow{2}{*}{WordNLM}}  & \multicolumn{2}{c}{\multirow{2}{*}{Frequency}}\\
% %	    &\multicolumn{2}{c|}{\emph{LSTM}}&\multicolumn{2}{c|}{\emph{RNN}} & & & \\ \hline
% %% eadj-aonoun
% %	    Noun Gender & 96.6&89.6  & 84.4&73.9 & 99.1&95.6 & 100.0 & 0.0\\
% %%      adv-aoadj
% %	    Adj.~Gender & 98.9&100.0 & 100.0&97.8 & 98.9&100.0 & 55.7 & 44.3 \\
% %% adv-aeadj
% %	    Adj.~Number & 99.0&99.0 & 99.0&70.0 & 100.0&100.0 & 86.7 & 13.3 \\
% %
%       \end{tabular}
%     \end{center}
%   \end{small}
%   \caption{\label{tab:ital-agr-results} Italian agreement results.} % For each model and test, we report percentage accuracy on two stimulus classes (masculine/feminine for gender, singular/plural for number).}
% \end{table}


\paragraph{Article-adjective number agreement}
Finally, we constructed a version of the last test that probed number agreement. For feminine forms, it is possible to compare same-length phrases such as:
\ex.\ag. la meno \{\underline{aliena},\ aliene\} \\
the\ (s.) less alien\ one(s) \\
\bg. le meno \{aliena,\ \underline{aliene}\} \\
the\ (p.) less alien\ one(s) \\

%\begin{enumerate}[label={(\arabic*)}]
%	\item 
%\begin{tabular}[t]{lllllll}
%	a. & la & meno & \{ \underline{aliena}, aliene \} \\
%   &  the (s.)& less & alien one(s)  \\
%	b. & le & meno & \{ aliena, \underline{aliene} \} \\
%    &the (p.)& less & alien one(s) \\
%\end{tabular}
%\end{enumerate}
% /checkpoint/mbaroni/char-rnn-exchange/candidate_adv_aeadj_testset.txt
Stimulus selection was as in the last experiment, but we used a 500-occurrences
threshold for adjectives, as feminine plurals are less common, obtaining 99 pairs. Again, no adverb-adjective combination was attested. %  Further, we manually
There were no OOV items for the WordNLM. %
% removed adjectives that did not combine well semantically with the
% adverbs under consideration (\emph{pi{\`u}, meno, tanto}).
Results are shown on the third line of
Table~\ref{tab:ital-agr-results}; the LSTMs perform almost perfectly,
and the RNN is strongly above chance.

